Spatial Analysis

### 2022-01-16 Scripts/spatial_analisis.Rmd
Included all ports for sensitivity analysis

    "westport, ma"

@@

    41.49267875746873
  ),
  lon = c(
    -71.48323250872187,
    -76.66239630117921,
    -76.35038306859545,
    -73.99190094110679,
    -76.48565862613168,
    -74.0763054899462,
    -71.93585836088813,
    -76.74333419560425,
    -75.61121671722921,
    -70.91580669134055,
    -74.90280944790463,
    -76.66793114333704,
    -75.35947580478219,
    -76.08680452670508,
    -71.9223721359251,
    -74.11329310115902,
    -75.05089736920318,
    -75.06397021718345,
    -70.22937554378885,
    -70.7126760833714,
    -75.38415668579887,
    -74.68797202847871,
    -75.06343692610851,
    -75.94328398140065,
    -72.50987544040999,
    -72.59899214258269,
    -71.19474641579107, 
    -72.0829697106489,
    -72.11879306740798,
    -74.09927831868308,
     -69.95466452556448,
    -70.13193663798509,
    -70.60001340709665,
     -73.59162509402208,
    -69.95617277257985,
     -71.32263326975122,
     -73.5763748512927,
     -72.4420929172018,
    -71.05551342392039
  )
) %>% 
  separate(port, into = c("port_name","state_postal"), sep = ',') %>% 
  mutate(port_name = str_to_lower(port_name),
         state_postal = str_squish(state_postal))

@@

# Check for missing ports (Should be empty!)
noaa_ports_complete %>% 
  filter(tresh == "75th",
    is.na(lat)) %>% 
  group_by(port_name,state_postal) %>% 
  summarise(n()) %>% 
  View()

# Save data for future analysis
# write_csv(noaa_ports_complete,
#           my_path("D","Partial", name = "top_ports.csv")
#           )

@@

@@

# Old code

>>>>

    "westport, ma",
    "east haven, ct", # 41.287588297369965, -72.91332498109327
    "menemsha, ma", #41.35483795676015, -70.76878790249602
    "sandwich (census name for sandwich center), ma", #41.773295466525006, -70.4834693734216
    "niantic (east lyme (sta.)), ct", #41.307802578709925, -72.18573251980143
    "chilmark, ma", # 41.33168444645112, -70.73421932978907
    "edgartown, ma", # 41.43835263574402, -70.49271845442495
    "harwich port, ma", # 41.66230920340751, -70.05980519928022
    "hyannis, ma", # 41.62905544508146, -70.29939641433006
    "mattapoisett, ma", # 41.65055975280539, -70.81223286674746
    "menemsha, ma", # 41.373297740713404, -70.77670726558624
    "center moriches, ny", # 40.782258285123575, -72.7953069671706
    "east hampton, ny", # 41.11361718020251, -72.06705712645356
    "greenport, ny", # 41.09916125257237, -72.35456699786954
    "island park, ny", # 40.94632184498529, -73.72913173589376
    "mount sinai, ny", # 41.01174251897529, -73.03449296418835
    "wainscott, ny", # 40.91995090087518, -72.22936945904769
    "bristol, ri", # 41.65577918701731, -71.28875398475536
    "jamestown, ri", # 41.470526163808394, -71.37037477616862 
    "north kingstown (local name wickford), ri", # 41.572678906576364, -71.43055123261533
    "portsmouth, ri", # 41.59982450656618, -71.22606882143374
    "south kingstown (town of), ri", # 41.60580919505512, -71.22689676246267
    "tiverton, ri", # 41.61012807350179, -71.21924759566026
     "warwick (rr name apponaug), ri", # 41.684523257387276, -71.44148310924662
    "westerly (rr name apponaug), ri", # 41.35954244353175, -71.83754886478252
    "westerly (census name westerly center), ri", # 41.35954244353175, -71.83754886478252
    "accomac, va", # 37.772002695051725, -75.82419557195219
    "little wicomico river, va", #37.89065111324239, -76.28371085150121
    "northampton (county), va",  # 37.019536098970725, -76.26084869871761
    "northumberland (county), va" # 37.82813770009578, -76.30849827818871

@@

    41.49267875746873,
    41.287588297369965,
    41.35483795676015,
    41.773295466525006,
    41.307802578709925,
    41.33168444645112,
    41.43835263574402,
    41.66184849328297,
    41.62905544508146,
    41.65055975280539,
    41.373297740713404,
    40.782258285123575,
    41.11361718020251,
    41.09916125257237,
    40.93886056049701,
    41.01174251897529,
    40.91995090087518,
    41.65577918701731,
    41.470526163808394,
    41.572678906576364,
    41.59982450656618,
    41.60580919505512,
    41.61012807350179,
    41.684523257387276,
    41.35954244353175,
    41.35954244353175,
    37.772002695051725,
    37.89065111324239,
    37.019536098970725,
    37.82813770009578

  ),
  lon = c(
    -71.48323250872187,
    -76.66239630117921,
    -76.35038306859545,
    -73.99190094110679,
    -76.48565862613168,
    -74.0763054899462,
    -71.93585836088813,
    -76.74333419560425,
    -75.61121671722921,
    -70.91580669134055,
    -74.90280944790463,
    -76.66793114333704,
    -75.35947580478219,
    -76.08680452670508,
    -71.9223721359251,
    -74.11329310115902,
    -75.05089736920318,
    -75.06397021718345,
    -70.22937554378885,
    -70.7126760833714,
    -75.38415668579887,
    -74.68797202847871,
    -75.06343692610851,
    -75.94328398140065,
    -72.50987544040999,
    -72.59899214258269,
    -71.19474641579107, 
    -72.0829697106489,
    -72.11879306740798,
    -74.09927831868308,
    -69.95466452556448,
    -70.13193663798509,
    -70.60001340709665,
    -73.59162509402208,
    -69.95617277257985,
    -71.32263326975122,
    -73.5763748512927,
    -72.4420929172018,
    -71.05551342392039,
    -72.91332498109327,
    -70.76878790249602,
    -70.4834693734216,
    -72.18573251980143,
    -70.73421932978907,
    -70.49271845442495,
    -70.05918851677775,
    -70.29939641433006,
    -70.81223286674746,
    -70.77670726558624,
    -72.7953069671706,
    -72.06705712645356,
    -72.35456699786954,
    -73.71669826711323,
    -73.03449296418835,
    -72.22936945904769,
    -71.28875398475536,
    -71.37037477616862,
    -71.43055123261533,
    -71.22606882143374,
    -71.22689676246267,
    -71.21924759566026,
     -71.44148310924662,
     -71.83754886478252,
    -71.83754886478252,
     -75.82419557195219,
     -76.28371085150121,
     -76.26084869871761,
     -76.30849827818871
  )
) %>% 
  separate(port, into = c("port_name","state_postal"), sep = ',') %>% 
  mutate(port_name = str_to_lower(port_name),
         state_postal = str_squish(state_postal))

@@

# Check for missing ports (Should be empty!)
noaa_ports_complete %>% 
  filter(
         is.na(lat)) %>%
  group_by(port_name,state_postal) %>% 
  summarise(n()) %>% 
  View()

# Save data for future analysis
write_csv(noaa_ports_complete,
          my_path("G","AcrossBoundaries/Data/Partial", name = "top_ports.csv")
          )

@@

my_path("G","AcrossBoundaries/Data/Partial","top_ports.csv", read = T) %>% 
  filter(is.na(lat)) %>% 
  group_by(port_name,state_postal,lat,lon) %>% 
  tally() %>% 
  View()

@@

# Sensitivity analysis

## Top ports sensitivity

```{r sen_data}
# Estimate distance between points

top_ports_sen <- my_path("G","AcrossBoundaries/Data/Partial","top_ports.csv", read = T)

eez_sf <- st_read(my_path("G", extra_path = "Spatial/SAU/SAU_Shapefile", name = "SAUEEZ_July2015.shp")) %>% 
  st_transform(crs = 4326) %>% # 4326
  filter(Name == "USA (East Coast)") %>% 
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) #0.1 for paper
```

### Number of ports per state and sen

```{r number}
# Number of ports per tresh

top_ports_sen %>% 
  group_by(species_name, state_postal,tresh) %>% 
  tally() %>% 
  # View()
  ggplot() +
  geom_bar(
    aes(
      x = tresh,
      y = n,
      fill = tresh
    ),
    stat = "identity"
  ) +
  facet_grid(species_name~state_postal) +
  labs(y = "Number of ports")

### Number of ports per state and sen

```{r data_prep}

port_sf <- st_as_sf(top_ports_sen,
                    coords =c("lon","lat"),
                    crs = 4326)

# Expand grid

# Expand the grid
ne_grid <- expand.grid(
  lon = seq(from = -82.57346, to = -62.88543, by = 0.3),
  lat = seq(from = 29.77459, to = 49.19141 , by = 0.3)
) %>% 
  rowid_to_column("index")

# Crop grid to EEz
grid_fp_sf <- st_as_sf(ne_grid,
                       coords = c("lon", "lat"),
                       crs = 4326) %>% 
  st_join(port_bf) %>% # join to port sf
  filter(!is.na(port_name)) #%>%
# distinct(index,port_name, .keep_all = TRUE) #removes like 400K overlapping rows

# Create data frame for future computations
# Note, will be used in next chunk
grid_fp_bf_dt <- as.data.frame(grid_fp_sf) %>%
  select(index,port_name,state_postal,species_name,tresh)

#### Numbers

```{r numbers_per_tresh}

sens_plot <- grid_fp_bf_dt %>% 
  group_by(species_name,state_postal,Threshold = tresh) %>% 
  summarise(n = n(),
            nuni = length(unique(as.character(index)))
  ) %>% 
  ggplot() +
  geom_bar(
    aes(
      x = Threshold,
      y = nuni,
      fill = Threshold
    ),
    stat = "identity"
  ) +
  facet_grid(species_name~state_postal) +
  my_ggtheme_p(leg_pos = "right",
               ax_tx_s = 11
               ) +
  theme(axis.text.x = element_blank(),
        strip.background = element_rect(fill = "grey"))+
  labs(y = "Number of grid-cells (n)", x = "Threshold") +
  scale_fill_brewer(palette = "Set3")

ggsave(filename = "tresh_sens_plot.png",
       sens_plot)

```
# Old code
